The problem and promise of scale in multilayer animal social networks

### 2020-02-11 paper/manuscript.Rmd
getting thoughts down and reflowing conc

<!--QW: I am not very happy with this paragraph, but it's a start -->
Multilayer networks are complicated in that they can incorporate data as varied as social interactions, landscape features, and seasons, all of which exist at different scales and units of measurement. 
Our analysis of caribou multilayer networks incorporated high resolution GPS telemetry data and
spatial landcover data is grounded in the context of observed animal social networks, as the scales we chose to explore are ones that can be observed as has traditionally been done.

>>>>

<!--QW: I am not very happy with this paragraph, but it's a start -->
Multilayer networks are complicated in that they can incorporate data as varied as social interactions, landscape features, and seasons, all of which exist at different scales and units of measurement. 
Our analysis of caribou multilayer networks incorporated high resolution GPS telemetry data and
spatial landcover data is grounded in the context of observed animal social networks, as the scales we chose to explore are ones that can be observed as has traditionally been done.
<!-- JWT: I'm having a hard time getting to where I want to go, but basically I want to highlight that using GPS relocation data is reflective of more traditional observed networks like they wanted when they accepted our abstract, and this provides opportunities for social networks, particularly multilayer networks. It may be easier to scale relocation data and other landscape variables and can link to smaller scale observed interactions, providing a bridge between different types of data. -->
